%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Bhavan Naik} \\ \vspace{1pt}
    \small (+91)8805928641 $|$ \href{mailto:bhavannaik@gmail.com}{\underline{bhavannaik@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bhavan-naik/}{\underline{linkedin.com/in/bhavan-naik/}} $|$
    \href{https://github.com/Bhavan-Naik}{\underline{github.com/Bhavan-Naik}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer in Test}{Jul 2023 -- Present}
      {CoinDCX}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive socket sanity module, automating previously manual processes reducing labor and time requirements.}
        \resumeItem{Designed and implemented a data executor for the performance platform, optimizing and streamlining data handling processes.}
        \resumeItem{Engineered test suites for gRPC and REST API evaluations, enhancing the reliability and robustness of API functionalities.}
        \resumeItem{Contributed to the troubleshooting and setup of the performance platform, ensuring seamless and efficient operations.}
        \resumeItem{Awarded multiple quarterly performance recognitions for demonstrating exceptional productivity to company objectives.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Security Operations Engineer}{Jul 2022 -- Mar 2023}
      {Zoom Video Communications}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Automated GCP log streaming process using Python and Shell scripts, streamlining and optimizing log management systems.}
        \resumeItem{Developed a streamlined Ansible playbook for Zookeeper management, improving system reliability and operational efficiency.}
        \resumeItem{Developed a Python-based automation for LastPass password management, enhancing security protocols and workflow efficiency.}
        \resumeItem{Diagnosed and remediated bugs in Linux/Unix systems, ensuring the integrity and stability of the system environment.}
        \resumeItem{Participated as a member of Happy Crew, facilitating and coordinating numerous team-building events and activities.}
    \resumeItemListEnd

    \resumeSubheading
      {Data Science and Business Analytics Intern}{Jul 2021 -- Aug 2021}
      {The Sparks Foundation}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Exploratory Data Analysis on IPL Dataset using Python and Jupyter.}
      \resumeItemListEnd

    \resumeSubheading
      {Deep Learning Intern}{Jun 2021 -- Jul 2021}
      {Grroom}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Worked on web scraping, model building and model testing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PES University}{Jul 2018 -- Sep 2022}
      {Bachelor of Technology in Computer Science and Engineering}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{CGPA: 8.31/10.0 [First Class with Distinction]}
        \resumeItem{Specialization: Machine Learning and Data Science}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeItemListStart
      \resumeItem
          {Twitter Scraping (Historical and Live Streaming) Using Python \& Kafka 
}{}
      \resumeItem
          {Fully functional Banking System using MSSQL and MySQL}{}
      \resumeItem
          {Full fledged Knowledge Repository Website}{}
      \resumeItem
          {JavaScript Mini-Compiler {using Yacc and Lex}}{}
      \resumeItem
          {Smart Classroom Environment {IoT-based Project}}{}
      \resumeItemListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, C/C++, JavaScript, HTML/CSS} \\
     \textbf{Cloud}{: Amazon Web Services, Google Cloud Platform, Microsoft Azure} \\
     \textbf{DBMS}{: SQL (MySQL, MSSQL, Postgres), R, MongoDB} \\
     \textbf{BigData}{: Hadoop, HIVE, Kafka, Zookeeper, Spark, PySpark, Apache NiFi} \\
     \textbf{Dev Tools}{: Git, Docker, Kubernetes, Jenkins, VS Code, PyCharm, Datadog, Grafana} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
